cardinalR: Generating interesting high-dimensional data structures

### 2025-09-17 paper-cardinalR.Rmd
Added reference for branching data

A branching structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:branch)"} else { "Figure \\@ref(fig:branch-proj)"})`) captures trajectories that diverge or bifurcate from a common origin, similar to processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometries, numbers of points, and number of branches. Although these functions can generate multiple branches, they do not produce a formal *multicluster* dataset: the branches form a single connected structure, with multiple visually distinct arms rather than independent clusters. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.

>>>>

A branching structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:branch)"} else { "Figure \\@ref(fig:branch-proj)"})`) captures trajectories that diverge or bifurcate from a common origin, similar to processes such as cell differentiation in biology (@trapnell2014). We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometries, numbers of points, and number of branches. Although these functions can generate multiple branches, they do not produce a formal *multicluster* dataset: the branches form a single connected structure, with multiple visually distinct arms rather than independent clusters. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.

### 2025-09-17 paper-cardinalR.tex
Added reference for branching data

A branching structure (Figure \ref{fig:branch-proj}) captures trajectories that diverge or bifurcate from a common origin, similar to processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometries, numbers of points, and number of branches. Although these functions can generate multiple branches, they do not produce a formal \emph{multicluster} dataset: the branches form a single connected structure, with multiple visually distinct arms rather than independent clusters. Table \ref{tab:branching-tb-pdf} outlines these functions. The main arguments of the functions described in Table \ref{tab:arg-branching-tb-pdf}.

>>>>

A branching structure (Figure \ref{fig:branch-proj}) captures trajectories that diverge or bifurcate from a common origin, similar to processes such as cell differentiation in biology (\citet{trapnell2014}). We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometries, numbers of points, and number of branches. Although these functions can generate multiple branches, they do not produce a formal \emph{multicluster} dataset: the branches form a single connected structure, with multiple visually distinct arms rather than independent clusters. Table \ref{tab:branching-tb-pdf} outlines these functions. The main arguments of the functions described in Table \ref{tab:arg-branching-tb-pdf}.
